Cognate Priming

### 2022-12-21 docs/index.qmd
Render Quarto report in targets workflow

---
title: "Cognate Priming"
subtitle: "Lab notes"
date: "Updated: `r format(Sys.Date(), '%Y/%m/%d')`"
authors:
  - name: Gonzalo Garcia-Castro
    orcid: 0000-0002-8553-4209
    email: gonzalo.garciadecastro@upf.edu
    corresponding: true
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
        address: Ramon Trias fargas 25-27
        city: Barcelona
        state: Spain
        postal-code: 08005
abstract: "Previous studies have provided evidence that lexical access is language non-selective in bilinguals: recognising and producing words in one language activates lexical representations of words in the other language (e.g., Costa et al., 2000; Thierry & Wu, 2007). It has been suggested that this parallel activation is already present during toddlerhood (Jardak & Byers-Heinlein, 2019; Von Holzen & Mani, 2012), but it is unclear how it impacts the developing lexicon. In the present study, we tested Catalan-Spanish and English-Spanish bilinguals in a word recognition task, in which they were presented with words in their dominant language exclusively. In each trial, two pictures were presented side-by-side and one of them was named (target picture). Participants' visual preference for the named picture was taken as an indicator of word recognition. Each pair of pictures was preceded by the presentation of a silent image (prime picture). We designed three types of trials: (1) cognate trials in which prime and target labels shared phonological onset and the prime label was a cognate (e.g., flower-flor / fork), (2) non-cognate trials, in which prime and target labels shared phonological onset but the prime label was a non-cognate (e.g., frog-rana / fork), and (3) unrelated trials, in which prime and target labels did not share onset (unrelated trials; car-coche / fork). In line with previous studies, we expected participants to generate implicit labels for the prime pictures, which should interfere with target word recognition when both words share phonological onset (e.g., Mani & Plunkett, 2011). Additionally, under the hypothesis that bilingual participants would activate labels for the prime pictures in both languages, we predicted that interference would be stronger after cognate primes (labels from both languages share phonological overlap with target word recognition) than after non-cognate primes (only the label in the target language share phonological overlap with target word recognition). We tested bilinguals (n = 46) and same-aged monolingual controls, n = 123) at three age points (21, 25, and 30 months) to investigate how any cross-language priming effect emerged or changed across these ages."
format:
    html:
        link-external-newwindow: true
        number-offset: 0
        code-fold: true
        code-overflow: scroll
        code-line-numbers: true
        code-copy: hover
        reference-location: margin
        execute-dir: "C:/Users/U155880/Documents/trajectories/"
    pdf: default
    docx:
        reference-doc: reference.docx
fig-dpi: 1000
warning: false
echo: false
toc: true
colorlinks: true
number-sections: true
bibliography: "references.bib"
csl: "apa7.csl"
---

```{r}
#| label: setup
tar_load_globals()
tar_load_everything()

@@

options(
	ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
	ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
	ggplot2.discrete.fill = clrs[c(1, 4, 5)],
	ggplot2.discrete.colour = clrs[c(1, 4, 5)],
	ggplot2.continuous.fill = ggplot2::scale_color_gradient,
	ggplot2.continuous.colour = ggplot2::scale_color_gradient
)

@@

	cols_label(doe_mean_catalan_monolingual = "Catalan (%)",
			   doe_mean_catalan_bilingual = "Catalan (%)",
			   doe_mean_spanish_monolingual = "Spanish (%)",
			   doe_mean_spanish_bilingual = "Spanish (%)") %>% 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners())) %>% 
	tab_style(cell_text(size = "small"),
			  list(cells_body(),
			  	 cells_stub()))
```

@@

```{r}
#| label: fig-stimuli-category 
#| fig-height: 7
#| fig-width: 12
stimuli %>% 
	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
	pivot_longer(c(semantic_category_prime, semantic_category_target),
				 names_to = "role",
				 values_to = "semantic_category") %>% 
	mutate(role = str_to_sentence(str_remove(role, "semantic_category_"))) %>% 
	drop_na(trial_type, semantic_category) %>% 
	count(trial_type, test_language, role, semantic_category, name = "sum") %>% 
	right_join(expand(., trial_type,  test_language,  role,  semantic_category)) %>%
	replace_na(list(sum = 0)) %>% 
	group_by(trial_type, test_language, role) %>% 
	mutate(n =  sum(sum), prop = sum/n) %>% 
	ungroup() %>% 
	ggplot() +
	aes(x = prop,
		y = reorder_within(semantic_category, 
						   desc(prop), 
						   list(trial_type, role, test_language)),
		fill = test_language,
		order = prop) + 
	facet_wrap(trial_type~role~test_language,
			   scales = "free_y",
			   labeller = label_wrap_gen(multi_line = FALSE)) +
	geom_col(colour = "white",
			 position = position_dodge(),
			 width = 1) +
	labs(x = "% of trials",
		 y = "Trial type",
		 colour = "Trial type",
		 fill = "Trial type") +
	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
	scale_y_reordered() +
	theme(legend.position = "none",
		  legend.title = element_blank(),
		  axis.text.y = element_text(size = 9, hjust = 1),
		  axis.text.x = element_text(size = 8, hjust = 1),
		  axis.title.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  plot.caption = element_text(size = 10, hjust = 0),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		  strip.text = element_text(size = 10))
```

@@

We collected vocabulary data from participants. In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment. In Barcelona, participants were sent the online vocabulary inventory [BVQ](https://github.com/gongcastro/bvqdev) immediately after the appointment, and were given two weeks to fill it. In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language. In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists. All checklists included the words involved in the trial lists. When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*. Each response to either checklist was aggregated to produce several vocabulary measures:

@@

@@

**Parameters**:

$$
\begin{align}
y_{ij} =&~ (\beta_{0} + \beta_{0p} + \beta_{0i}) ~+~ ... \\ 
& (\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} ~+~ ... \\
& (\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} ~ + ~ ... \\
& (\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} ~ + ~ ... \\
& (\beta_{4} + \beta_{4i}) \times Group_{pi} ~+~ ... \\
& (\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) ~+~ ... \\
& (\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) ~+~ ... \\
& (\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) ~+~ ... \\
& (\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) ~+~ \\ & \sigma^2_{e}
\end{align}
$$

**Priors**:

$$
\begin{align}
\beta_0 \sim~ & \mathcal{N}(0, 1) \\
\beta_{1-8} \sim~ &\mathcal{N}(0, 1) \\
\sigma_m, ~\sigma^2,~ \sigma^2_p,~ \sigma^2_i \sim~ & exp(2) \\
\rho \sim ~&  LKJ(2)
\end{align}
$$

### Prior expected predicted mean

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, list, trial, trial_type,
					   freq_target, freq_prime, familiarity_prime, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status != "Valid",  "Excluded", valid_status)) %>% 
	drop_na() %>% 
	group_by(trial_type, valid_status, age_group) %>% 
	summarise(n = n(),
			  across(matches("freq_|familiarity_"),
			  	   lst(mean, sd)),
			  .groups = "drop") %>% 
	pivot_wider(names_from = valid_status,
				values_from = c(n, matches("freq_|familiarity_")),
				values_fill = 0) %>%
	clean_names() %>% 
	relocate(age_group, trial_type, n_valid, n_excluded, 
			 matches("_valid")) %>%

	gt(rowname_col = "trial_type", groupname_col = "age_group") %>% 
	fmt_number(matches("n_"), decimals = 0) %>% 
	fmt_number(matches("freq_"), decimals = 1) %>% 
	fmt_percent(matches("familiarity"), decimals = 1) %>% 
	tab_spanner("N", matches("n_")) %>% 
	tab_spanner("Prime familiarity", matches("familiarity_?prime_")) %>%
	tab_spanner("Target familiarity", matches("familiarity_?target_")) %>% 
	tab_spanner("Prime frequency", matches("freq_?prime_")) %>% 
	tab_spanner("Target frequency", matches("freq_?target_")) %>%

	cols_merge_uncert(col_val = freq_prime_mean_valid, col_uncert = freq_prime_sd_valid) %>% 
	cols_merge_uncert(col_val = freq_prime_mean_excluded, col_uncert = freq_prime_sd_excluded) %>% 
	cols_merge_uncert(col_val = freq_target_mean_valid, col_uncert = freq_target_sd_valid) %>% 
	cols_merge_uncert(col_val = freq_target_mean_excluded, col_uncert = freq_target_sd_excluded) %>%

	cols_merge_uncert(col_val = familiarity_prime_mean_valid, col_uncert = familiarity_prime_sd_valid) %>% 
	cols_merge_uncert(col_val = familiarity_prime_mean_excluded, col_uncert = familiarity_prime_sd_excluded) %>% 
	cols_merge_uncert(col_val = familiarity_target_mean_valid, col_uncert = familiarity_target_sd_valid) %>% 
	cols_merge_uncert(col_val = familiarity_target_mean_excluded, col_uncert = familiarity_target_sd_excluded) %>%

	cols_label(n_excluded = "⨯",
			   n_valid = "✓",
			   freq_prime_mean_valid = "✓",
			   freq_prime_mean_excluded = "⨯",
			   freq_target_mean_valid = "✓",
			   freq_target_mean_excluded = "⨯",
			   familiarity_prime_mean_valid = "✓",
			   familiarity_prime_mean_excluded = "⨯",
			   familiarity_target_mean_valid = "✓",
			   familiarity_target_mean_excluded = "⨯") %>% 
	summary_rows(groups = TRUE,
				 columns = matches("freq_") ,
				 fns = list("Mean" = ~mean(.)), 
				 formatter = fmt_number,
				 decimals = 0) %>% 
	summary_rows(groups = TRUE,
				 columns = matches("familiarity_"), 
				 fns = list("Mean" = ~mean(.)),
				 formatter = fmt_percent,
				 decimals = 1) %>% 
	grand_summary_rows(columns = matches("n_"),
					   fns = list("N" = ~sum(.)),
					   formatter = fmt_number,
					   decimals = 0) %>% 
	tab_style(cell_text(align = "center"),
			  cells_column_labels()) %>% 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners(),
			  	 cells_grand_summary(),
			  	 cells_row_groups(),
			  	 cells_stub_grand_summary(),
			  	 cells_stub_summary()))

@@

```{r model-comparison, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

# model_comparison <- waics_l1 %>% 
# 	map("estimates") %>% 
# 	map(function(x) rownames_to_column(as.data.frame(x), "variable")) %>% 
# 	bind_rows(.id = "model") %>%
# 	clean_names() 
# 	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
# 	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
# 	mutate(
# 		model = c(
# 			"Intercept",
# 			"... + Trial type",
# 			"... + Group \u00d7Trial type\u00d7Group",
# 			"... + Vocab. + Trial type\u00d7Vocab. + Group\u00d7Vocab.",
# 			"... + Trial type\u00d7Vocab. + Group\u00d7Vocab. + Trial type\u00d7Group\u00d7Vocab."
# 		)
# 	) %>% 
# 	gt() %>% 
# 	fmt_number(-model) %>% 
# 	tab_spanner("WAIC", matches("waic")) %>% 
# 	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
# 	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
# 	cols_label(
# 		model = "Model",
# 		estimate_elpd_waic = "Estimate",
# 		estimate_waic = "Estimate",
# 		estimate_p_waic = "Estimate",
# 		se_elpd_waic = md("*SE*"),
# 		se_waic = md("*SE*"),
# 		se_p_waic = md("*SE*"),
# 	) %>% 
# 	cols_align("right", "model") %>% 
# 	tab_style(
# 		cell_text(weight = "bold"),
# 		cells_column_spanners()
# 	) %>% 
# 	tab_style(
# 		cell_text(style = "italic"),
# 		cells_column_labels()
# 	)
# 
# gtsave(model_comparison, here("img", "model_comparison.png"))
# 
# 
# as_raw_html(model_comparison)

@@

```{r}
#| label: fixed-effects
#| fig-height: 10
#| fig-width: 12
post_draws <- gather_draws(fit_3, `b_.*`, regex = TRUE)

>>>>

---
title: "Cognate Priming"
subtitle: "Lab notes"
date: "Updated: `r format(Sys.Date(), '%Y/%m/%d')`"
authors:
  - name: Gonzalo Garcia-Castro
    orcid: 0000-0002-8553-4209
    email: gonzalo.garciadecastro@upf.edu
    corresponding: true
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
        address: Ramon Trias fargas 25-27
        city: Barcelona
        state: Spain
        postal-code: 08005
abstract: "Previous studies have provided evidence that lexical access is language non-selective in bilinguals: recognising and producing words in one language activates lexical representations of words in the other language (e.g., Costa et al., 2000; Thierry & Wu, 2007). It has been suggested that this parallel activation is already present during toddlerhood (Jardak & Byers-Heinlein, 2019; Von Holzen & Mani, 2012), but it is unclear how it impacts the developing lexicon. In the present study, we tested Catalan-Spanish and English-Spanish bilinguals in a word recognition task, in which they were presented with words in their dominant language exclusively. In each trial, two pictures were presented side-by-side and one of them was named (target picture). Participants' visual preference for the named picture was taken as an indicator of word recognition. Each pair of pictures was preceded by the presentation of a silent image (prime picture). We designed three types of trials: (1) cognate trials in which prime and target labels shared phonological onset and the prime label was a cognate (e.g., flower-flor / fork), (2) non-cognate trials, in which prime and target labels shared phonological onset but the prime label was a non-cognate (e.g., frog-rana / fork), and (3) unrelated trials, in which prime and target labels did not share onset (unrelated trials; car-coche / fork). In line with previous studies, we expected participants to generate implicit labels for the prime pictures, which should interfere with target word recognition when both words share phonological onset (e.g., Mani & Plunkett, 2011). Additionally, under the hypothesis that bilingual participants would activate labels for the prime pictures in both languages, we predicted that interference would be stronger after cognate primes (labels from both languages share phonological overlap with target word recognition) than after non-cognate primes (only the label in the target language share phonological overlap with target word recognition). We tested bilinguals (n = 46) and same-aged monolingual controls, n = 123) at three age points (21, 25, and 30 months) to investigate how any cross-language priming effect emerged or changed across these ages."
format:
    html:
        link-external-newwindow: true
        number-offset: 0
        code-fold: true
        code-overflow: scroll
        code-line-numbers: true
        code-copy: hover
        reference-location: margin
    pdf: default
    docx:
        reference-doc: reference.docx
fig-dpi: 1000
warning: false
echo: false
toc: true
colorlinks: true
number-sections: true
bibliography: "references.bib"
csl: "apa7.csl"
---

```{r}
#| label: setup
#| include: false

tar_load_everything() # load target objects

# load packages
library(dplyr)
library(tidyr)
library(stringr)
library(tibble)
library(purrr)
library(lubridate)
library(ggplot2)
library(gt)
library(tidybayes)
library(brms)
library(polypoly)
library(tidytext)
library(janitor)
library(forcats)
library(scales)
library(patchwork)
library(bvqdev)

@@

options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
	ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
	ggplot2.discrete.fill = clrs[c(1, 4, 5)],
	ggplot2.discrete.colour = clrs[c(1, 4, 5)],
	ggplot2.continuous.fill = ggplot2::scale_color_gradient,
	ggplot2.continuous.colour = ggplot2::scale_color_gradient)

@@

	cols_label(doe_mean_catalan_monolingual = "Catalan (%)",
			   doe_mean_catalan_bilingual = "Catalan (%)",
			   doe_mean_spanish_monolingual = "Spanish (%)",
			   doe_mean_spanish_bilingual = "Spanish (%)") %>% 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners())) %>% 
	tab_style(cell_text(size = "medium"),
			  list(cells_body(),
			  	 cells_stub()))
```

@@

::: {.panel-tabset}

#### Prime

```{r}
#| label: fig-stimuli-category-prime
#| fig-height: 7
#| fig-width: 12
stimuli %>% 
	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
	drop_na(trial_type, semantic_category_prime) %>% 
	count(trial_type, test_language, semantic_category_prime, name = "sum") %>% 
	right_join(expand(., trial_type,  test_language,  semantic_category_prime)) %>%
	replace_na(list(sum = 0)) %>% 
	group_by(trial_type, test_language) %>% 
	mutate(n =  sum(sum), prop = sum/n) %>% 
	ungroup() %>% 
	ggplot() +
	aes(x = prop,
		y = reorder_within(semantic_category_prime, desc(prop), list(trial_type, test_language)),
		fill = test_language,
		order = prop) + 
	facet_wrap(test_language~trial_type,
			   scales = "free_y",
			   labeller = label_wrap_gen(multi_line = FALSE)) +
	geom_col(colour = "white",
			 position = position_dodge(),
			 width = 1) +
	labs(x = "% of trials",
		 y = "Trial type",
		 colour = "Trial type",
		 fill = "Trial type") +
	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
	scale_y_reordered() +
	theme(legend.position = "none",
		  legend.title = element_blank(),
		  axis.text.y = element_text(size = 9, hjust = 1),
		  axis.text.x = element_text(size = 8, hjust = 1),
		  axis.title.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  plot.caption = element_text(size = 10, hjust = 0),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		  strip.text = element_text(size = 10))
```

#### Target

```{r}
#| label: fig-stimuli-category-target
#| fig-height: 7
#| fig-width: 12
stimuli %>% 
	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
	drop_na(trial_type, semantic_category_target) %>% 
	count(trial_type, test_language, semantic_category_target, name = "sum") %>% 
	right_join(expand(., trial_type,  test_language,  semantic_category_target)) %>%
	replace_na(list(sum = 0)) %>% 
	group_by(trial_type, test_language) %>% 
	mutate(n =  sum(sum), prop = sum/n) %>% 
	ungroup() %>% 
	ggplot() +
	aes(x = prop,
		y = reorder_within(semantic_category_target, desc(prop), list(trial_type, test_language)),
		fill = test_language,
		order = prop) + 
	facet_wrap(test_language~trial_type,
			   scales = "free_y",
			   labeller = label_wrap_gen(multi_line = FALSE)) +
	geom_col(colour = "white",
			 position = position_dodge(),
			 width = 1) +
	labs(x = "% of trials",
		 y = "Trial type",
		 colour = "Trial type",
		 fill = "Trial type") +
	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
	scale_y_reordered() +
	theme(legend.position = "none",
		  legend.title = element_blank(),
		  axis.text.y = element_text(size = 9, hjust = 1),
		  axis.text.x = element_text(size = 8, hjust = 1),
		  axis.title.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  plot.caption = element_text(size = 10, hjust = 0),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		  strip.text = element_text(size = 10))
```

@@

We collected vocabulary data from participants. In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI, @hamilton2000infant] two weeks before each appointment. In Barcelona, participants were sent the online vocabulary inventory [BVQ](https://github.com/gongcastro/bvqdev) immediately after the appointment, and were given two weeks to fill it. In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language. In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists. All checklists included the words involved in the trial lists. When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*. Each response to either checklist was aggregated to produce several vocabulary measures:

@@

### Data processing

@@

### Predictors

### Model

$$
\begin{aligned}
\textbf{Likelihood:} \\
y_{ij} &\sim \text{Bernoulli}(p)
\end{aligned}
$$ {#eq-likelihood}

where:

- $y$ is an observed response ($y \in \{\text{No, Understands, Understands and Says}\}$)
- $i$ is the participant index
- $j$ is the translation equivalent (TE) index
- $p$ is the probability f target looking ($p \in (0, 1)$)

$p$ is then estimated using a logit regression model as indicated in @eq-linear.

$$
\begin{aligned}
\textbf{Linear model:} \\
logit(p) = \text{ln} \frac{p}{1-p} &= (\beta_{0} + u_{0_{i}}) + \\
& (\beta_{1} + u_{1_{i}}) · \text{Age group}_{i} + & \\
& \beta_{2} · \text{Language Profile}_{i} + & \\
& (\beta_{3} + u_{2_{i}}) · \text{Trial type}_{i} + & \\
& \beta_{4} · (\text{Age group}_{i} \times \text{Language Profile}_{i}) & \\
& (\beta_{5} + u_{3_{i}}) · (\text{Age group}_{i} \times \text{Trial type}_{i}) + & \\
& \beta_{6} · (\text{Language Profile}_{ij} \times \text{Trial type}_{i}) & \\
& \beta_{7} · (\text{Age group}_{i} \times \text{Language Profile}_{i} \times \text{Trial type}_{i}) & \\
\end{aligned}
$$ {#eq-linear}

where:

- $i$ and $j$ index the participant and translation equivalent (TE)
- $\beta_{0_k}$ is the fixed coefficient of the regression model for the intercept of threshold $k$
- $u_{0_{i}}$ and $w_{0_{j}}$ are the by-participant and by-TE adjustments for $\beta_{0_{k}}$ (i.e., random intercepts), respectively
- $\beta_{1-8}$ are the fixed coefficients of the regression model for the predictors of interest
- $u_{1-8_{i}}$ and $w_{1-3_{j}}$ are the by-participant and by-TE adjustments for$\beta_{1-8}$ (i.e., random slopes), respectively

$$
\begin{aligned}
\\
\textbf{Prior:} \\
\beta_{0_{k}} &\sim \mathcal{N}(-0.25, 0.1) & [\mbox{Intercept/response category threshold}] \\
\beta_{1} &\sim \mathcal{N}(1, 0.1) & [\mbox{Age population-level coefficient}]\\
\beta_{2-8} &\sim \mathcal{N}(0, 1) & [\mbox{Rest of population-level coefficients}] \\
u_{0-8_{i}} &\sim \mathcal{N}(0, \sigma_{u_{0-8_{i}}}) & [\mbox{Participant-level coefficient variability}] \\
w_{0-3_{j}} &\sim \mathcal{N}(0, \sigma_{w_{0-3_{j}}}) & [\mbox{TE-level coefficient variability}] \\\\
&&\mbox{[Participant-level coefficient variability]} \\ \\
\Bigg(\begin{smallmatrix}
u_{k_{0}} \\ 
u_{1_{i}} \\ 
\vdots \\ 
u_{8_{i}} 
\end{smallmatrix}\Bigg) &\sim \mathcal{N} 
\Bigg(\Bigg(\begin{smallmatrix}0 \\
0 \\ 
\vdots \\
0\end{smallmatrix}\Bigg), \Sigma_{u}\Bigg) \\
\Sigma_{u} &= \Bigg(\begin{smallmatrix} \\
\rho_{u_{0}} & \rho_{u_{0}} \sigma_{u_{0_{k}}} \sigma_{u_{1}} & \dots & \rho_{u_{0}} \sigma_{u_{0}} \sigma_{w_{8}}\\ 
\rho_{u_{1}} \sigma_{u_{1}} \sigma_{u_{0}} & \rho_{u_{1}} & \dots & \rho_{u_{1}} \sigma_{u_{1}} \sigma_{u_{8}}\\ 
\vdots & \vdots & \vdots & \vdots \\
\rho_{8} \sigma_{u_{8}} \sigma_{u_{0_{k}}} & \dots & \dots & \rho_{u_{8}} \end{smallmatrix}\Bigg) \\
\sigma_{u_{0-8}} &\sim \mathcal{N_{+}}(1, 0.1) \\
\rho_{u} &\sim LKJcorr(2) \\
\\
&&\mbox{[TE-level coefficient variability]} \\ \\
\Bigg(\begin{smallmatrix}
w_{k_{0}}\\ 
w_{1_{j}} \\ 
\vdots \\ 
w_{3_{j}} 
\end{smallmatrix}\Bigg) &\sim \mathcal{N} \Bigg(\Bigg(\begin{smallmatrix}
0\\ 
0 \\ 
\vdots \\
0 
\end{smallmatrix}\Bigg), \Sigma_{w}\Bigg) \\
\Sigma_{w} &= \Bigg(\begin{smallmatrix} \\
\rho_{w_{0}} & \rho_{w_{0}} \sigma_{w_{0_{k}}} \sigma_{w_{1}} & \dots & \rho_{w_{0}} \sigma_{w_{0}} \sigma_{w_{3}}\\ 
\rho_{w_{1}} \sigma_{w_{1}} \sigma_{w_{0}} & \rho_{w_{1}} & \dots & \rho_{w_{1}} \sigma_{w_{1}} \sigma_{w_{3}}\\ 
\vdots & \vdots & \vdots & \vdots \\
\rho_{3} \sigma_{w_{3}} \sigma_{w_{0_{k}}} & \dots & \dots & \rho_{w_{3}} \end{smallmatrix}\Bigg) \\
\sigma_{w_{0-3}} &\sim \mathcal{N_{+}}(1, 0.1) \\
\rho_{w_{0-3}} &\sim LKJcorr(2)
\end{aligned}
$$ {#eq-prior}

@@

attrition %>% 
	left_join(distinct(participants, id, age_group, test_language, list, version, list)) %>% 
	left_join(distinct(stimuli, test_language, version, list, trial_id, trial_type,
					   freq_target, freq_prime, familiarity_prime, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status != "Valid",  "Excluded", valid_status)) %>% 
	drop_na() %>% 
	group_by(trial_type, valid_status, age_group) %>% 
	summarise(n = n(),
			  across(matches("freq_|familiarity_"), lst(mean, sd)),
			  .groups = "drop") %>% 
	pivot_wider(names_from = valid_status,
				values_from = c(n, matches("freq_|familiarity_")),
				values_fill = 0) %>%
	clean_names() %>% 
	relocate(age_group, trial_type, n_valid, n_excluded, 
			 matches("_valid")) %>%

	gt(rowname_col = "trial_type", groupname_col = "age_group") %>% 
	fmt_number(matches("n_"), decimals = 0) %>% 
	fmt_number(matches("freq_"), decimals = 1) %>% 
	fmt_number(matches("familiarity"), scale_by = 100, decimals = 1) %>%

	tab_spanner("N", c(n_valid, n_excluded)) %>%

	tab_spanner("Prime", id = 1, c(freq_prime_mean_valid, freq_prime_mean_excluded)) %>%
	tab_spanner("Target", id = 2, c(freq_target_mean_valid, freq_target_mean_excluded)) %>% 
	tab_spanner("Prime", id = 3, c(familiarity_prime_mean_valid, familiarity_prime_mean_excluded)) %>% 
	tab_spanner("Target", id = 4, c(familiarity_target_mean_valid, familiarity_target_mean_excluded)) %>%
	tab_spanner("Frequency", starts_with("freq_")) %>% 
	tab_spanner("Familiarity (%)", starts_with("familiarity_")) %>%

	cols_merge_uncert(col_val = freq_prime_mean_valid, col_uncert = freq_prime_sd_valid) %>% 
	cols_merge_uncert(col_val = freq_prime_mean_excluded, col_uncert = freq_prime_sd_excluded) %>% 
	cols_merge_uncert(col_val = freq_target_mean_valid, col_uncert = freq_target_sd_valid) %>% 
	cols_merge_uncert(col_val = freq_target_mean_excluded, col_uncert = freq_target_sd_excluded) %>% 
	cols_merge_uncert(col_val = familiarity_prime_mean_valid, col_uncert = familiarity_prime_sd_valid) %>% 
	cols_merge_uncert(col_val = familiarity_prime_mean_excluded, col_uncert = familiarity_prime_sd_excluded) %>% 
	cols_merge_uncert(col_val = familiarity_target_mean_valid, col_uncert = familiarity_target_sd_valid) %>%
	cols_merge_uncert(col_val = familiarity_target_mean_excluded, col_uncert = familiarity_target_sd_excluded) %>%

	cols_label(n_excluded = "Excluded",
			   n_valid = "Included",
			   freq_prime_mean_valid = "Included",
			   freq_prime_mean_excluded = "Excluded",
			   freq_target_mean_valid = "Included",
			   freq_target_mean_excluded = "Excluded",
			   familiarity_prime_mean_valid = "Included",
			   familiarity_prime_mean_excluded = "Excluded",
			   familiarity_target_mean_valid = "Included",
			   familiarity_target_mean_excluded = "Excluded") %>% 
	summary_rows(groups = TRUE,
				 columns = matches("freq_") ,
				 fns = list("Mean" = ~mean(.)), 
				 formatter = fmt_number,
				 decimals = 1) %>% 
	summary_rows(groups = TRUE,
				 columns = matches("familiarity_"), 
				 fns = list("Mean" = ~mean(.)),
				 formatter = fmt_number,
				 scale_by = 100,
				 decimals = 1) %>% 
	grand_summary_rows(columns = c(n_valid, n_excluded),
					   fns = list("N" = ~sum(.)),
					   formatter = fmt_number,
					   decimals = 0) %>% 
	grand_summary_rows(columns = matches("familiarity_"),
					   fns = list("Mean" = ~mean(.)),
					   formatter = fmt_number,
					   scale_by = 100,
					   decimals = 1) %>% 
	grand_summary_rows(columns = matches("freq_"),
					   fns = list("Mean" = ~mean(.)),
					   formatter = fmt_number,
					   decimals = 1) %>% 
	tab_style(cell_text(align = "center"),
			  cells_column_labels()) %>% 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners(),
			  	 cells_grand_summary(),
			  	 cells_row_groups(),
			  	 cells_stub_grand_summary(),
			  	 cells_stub_summary()))

@@

```{r}
#| label: tab-model-comparison
loos %>% 
	as_tibble(.name_repair = make_clean_names) %>% 
	rownames_to_column("model") %>% 
	relocate(
		model, 
		matches("diff"),
		matches("elpd_loo"),
		matches("p_loo"), 
		matches("looic")
	) %>%
	mutate(across(everything(), as.numeric),
		   model = attr(loos, "dimnames")[[1]]) %>% 
	select(-matches("subsampling")) %>% 
	gt(rowname_col = "model") %>%
	fmt_number(is.numeric, decimals = 1) %>% 
	cols_merge_uncert(col_val = elpd_diff, col_uncert = se_diff) %>% 
	cols_merge_uncert(col_val = elpd_loo, col_uncert = se_elpd_loo) %>% 
	cols_merge_uncert(col_val = p_loo, col_uncert = se_p_loo) %>% 
	cols_merge_uncert(col_val = looic, col_uncert = se_looic) %>% 
	cols_label(model = "Model",
			   elpd_loo = md("*ELPD*"),
			   p_loo = md("*p*"),
			   looic = md("*LOO-IC*"),
			   elpd_diff = md("Difference")) %>% 
	tab_source_note(md("Pareto-*k* estimates of all models were acceptable (*k* < 0.5)")) %>% 
	tab_style(cell_text(weight = "bold"),
			  cells_column_labels()) %>% 
	tab_style(cell_fill(color = "grey", alpha = 0.5),
			  cells_body(matches("diff"))) %>% 
	tab_style(cell_fill(color = clrs[4], alpha = 0.75),
			  cells_body(everything(), 1))
```

@@

::: {.panel-tabset}

#### Table

```{r}
#| label: tbl-fixed-effects
#| tbl-cap: "Summary of the posterior distribution of the Growth Curve Analysis model. We report the median and 95% highest density interval (*HDI*) of each fixed coefficient. The 95% interval indicates the range of values that contains the true value of the parameter with 95% probability. Values are in *logit* scale. Coefficients whose 95% HDI excludes zero are highlighted in red. Coefficients on the intercept indicate changes in overal proportion of target looking, coefficients in the linear term indicate changes in the overall slope of target looking growth across time, coefficients in the quadratic and cubic terms reflect the steepness of the rise and fall or of the rise, fall and rise, respectivey,  of the curve."
post_draws <- gather_draws(fit_3, `b_.*`, regex = TRUE)

str_repl <- c(
	"b_Intercept" = "Base",
	"b_ot1" = "Base",
	"b_ot2" = "Base",
	"b_ot3" = "Base",
	"b_age_group21_25" = "Age [21-25]",
	"b_age_group25_30" = "Age [25-30]",
	"b_lpmon_bil" = "Group",
	"b_trial_typerelated_unrelated" = "Prime (relatedness)",
	"b_trial_typecognate_noncognate" = "Prime (cognateness)",

	"b_age_group21_25:lpmon_bil" = "Age [21-25] × Group",
	"b_age_group25_30:lpmon_bil" = "Age [25-30] × Group",
	"b_age_group21_25:trial_typerelated_unrelated" = "Age [21-25] × Prime (relatedness)",
	"b_age_group21_25:trial_typecognate_noncognate" = "Age [21-25] × Prime (cognateness)",
	"b_age_group25_30:trial_typerelated_unrelated" = "Age [25-30] × Prime (relatedness)",
	"b_age_group25_30:trial_typecognate_noncognate" = "Age [25-30] × Prime (cognateness)",
	"b_lpmon_bil:trial_typerelated_unrelated" = "Group × Prime (relatedness)",
	"b_lpmon_bil:trial_typecognate_noncognate" = "Group × Prime (cognateness)",

	"b_age_group21_25:lpmon_bil:trial_typerelated_unrelated" = "Age [21-25] × Group × Prime (relatedness)",
	"b_age_group21_25:lpmon_bil:trial_typecognate_noncognate" = "Age [21-25] × Group × Prime (cognateness)",
	"b_age_group25_30:lpmon_bil:trial_typerelated_unrelated" = "Age [25-30] × Group × Prime (relatedness)",
	"b_age_group25_30:lpmon_bil:trial_typecognate_noncognate" = "Age [25-30] × Group × Prime (cognateness)"
)
